---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# compliment2

<!-- badges: start -->
<!-- badges: end -->

compliment2 generates randomized compliments about coding in R, along with
random goodbyes for when the coding session is over. Use it to brighten up
your console, your R scripts, or your colleagues' day.

## Installation

You can install the development version of compliment2 from
[GitHub](https://github.com/grcetmpk/compliment2) with:

``` r
# install.packages("pak")
pak::pak("grcetmpk/compliment2")
```

## Usage

`compliment_r()` generates a random compliment about coding in R:

```{r example-compliment}
library(compliment2)
compliment_r()
```

Request more than one at a time with the `n` argument:

```{r example-compliment-n}
compliment_r(3)
```

When it's time to log off, `farewell()` generates a random goodbye:

```{r example-farewell}
farewell()
```

## Acknowledgments

This package was developed at
[posit::conf 2026](https://posit-conf-2026.github.io/modern-r-workflow/),
following the Modern R Workflow workshop, and built with Posit AI Pass.

## License

compliment2 is released under the [MIT license](LICENSE.md).
